Fundamental measure theory for hard polyhedra.

### 2013-01-18 papers/polyhedra/paper.tex
add polyhedra citations Tested everything on node24.

Why study hard polyhedra? Hard spheres are the standard reference
system for essentially all fluids, but always have 12-fold
coordination.  A few very interesting liquids have tetrahedral
coordination, which is particularly significant when we consider the
freezing transition.  By studying hard polyhedra, we potentially can
develop a reference functional that can incorporate orientational
effects.

There have been several studies of non-spherical hard shapes.  At
least one omitted the rotational degrees of freedom (parallel hard
cubes, add citation).  At least one included the rotational degrees of
freedom, treating each orientation as a distinct species, resulting in
a density that exists in six dimensions rather than three, which was
applied to systems with a high aspect ratio, which undergo a nematic
transition.  It seems a good thing to have a density functional that
is more efficient, with fewer degrees of freedom to optimize.  In
particular, we are optimistic that one can do better for ``almost
spherical'' polyhedra.

@@

%\bibliography{paper}% Produces the bibliography via BibTeX.

>>>>

Why study hard polyhedra? Hard spheres are the standard reference
system for essentially all fluids, but always have 12-fold
coordination.  A few very interesting liquids have tetrahedral
coordination, which is particularly significant when we consider the
freezing transition.  By studying hard polyhedra, we potentially can
develop a reference functional that can incorporate orientational
effects.  (For reference, an excellent review of hard-particle systems
is the following book chapter~\cite{tarazona2008chapter}.)

There have been several studies of non-spherical hard shapes.  At
least one omitted the rotational degrees of
freedom~\cite{cuesta1996cubes, cuesta1997dimensional,
  cuesta1997fundamental, buhot1998numerical, martinez1999fundamental,
  capitan2007hexagons,
  capitan2008phase, martinez2008fundamental}.  At least one included
the rotational degrees of freedom, treating each orientation as a
distinct species, resulting in a density that exists in more
dimensions than three, which was applied to systems with a high aspect
ratio, which undergo a nematic transition~\cite{schmidt2001density,
  esztermann2006density, harnau2008structure, hansen2009fundamental,
  hansen2010tensorial}.  It seems a good thing to have a density
functional that is more efficient, with fewer degrees of freedom to
optimize.  In particular, we are optimistic that one can do better for
``almost spherical'' polyhedra.

There has been simulation of the melting of hard cubes, demonstrating
that allowing rotational disorder leads to a first-order phase
transition~\cite{jagla1998melting}, which is not seen in parallel hard
cubes.  There has been another study of melting of parallel hard
cubes~\ref{groh2001closer}.

@@

\bibliography{paper}% Produces the bibliography via BibTeX.
